Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-14 egpaper_final.tex
added pascal12 cnn+our figures. modified plots : larger fonts, thicker lines

@@

\begin{figure}[t]
  \begin{center}
  \begin{tabular}{cc}
     \includegraphics[width=0.5\linewidth]{whotime} & 
     \includegraphics[width=0.5\linewidth]{speedup}\\
     (a) & (b) \\
 \end{tabular}
  \end{center}
  \caption{Comparison of HOG variants generation time and final }
  \label{fig:whotime}
\end{figure}
[Figure spectral analysis]

@@

\section{Continuous Viewpoint and Focal Length Estimation for Fine Tuning}

@@

% there are several advantages that was not possible such as \textbf{on-the-fly} template generation and making large number of templates  
\begin{figure}[t]
 \begin{center}
    \includegraphics[width=0.9\linewidth]{tuning2} 
    \includegraphics[width=0.9\linewidth]{tuning} 
 \end{center}
 \caption{Effect of fine tuning. (left) original image, (middle) initial detection, (right) continuous fine tuning}
 \label{fig:tuning}
\end{figure}

@@

>>>>

% custom commands
\newcommand{\scream}[1]{{\bf *** #1! ***}}

@@

\begin{figure}[t]
  \begin{center}
  \begin{tabular}{cc}
     \includegraphics[width=0.5\linewidth]{whotime} & 
     \includegraphics[width=0.5\linewidth]{speedup}\\
     (a) & (b) \\
 \end{tabular}
  \end{center}
  \caption{Comparison of HOG variants generation time and final }
  \label{fig:whotime}
\end{figure}

[Figure spectral analysis]

@@

\section{Continuous Viewpoint and Focal Length Estimation for Fine Tuning}
\label{sec:fine}

@@

% there are several advantages that was not possible such as \textbf{on-the-fly} template generation and making large number of templates

\begin{figure}[t]
\centering
    \includegraphics[width=0.7\linewidth]{tuning2} \\ [-5pt]
    \caption{Different modes of Metropolis Hasting proposals, see Section \ref{sec:fine}}
 \label{fig:tuningmode}
\end{figure}

\begin{figure}[t]
 \begin{center}
    \setlength\tabcolsep{0pt}
    \begin{tabular}{ccc}
    % \includegraphics[width=0.9\linewidth]{tuning} 
   \includegraphics[width=0.33\linewidth]{tuning/1.png} &
   \includegraphics[width=0.33\linewidth]{tuning/2.png} &
   \includegraphics[width=0.33\linewidth]{tuning/3.png} \\[-5pt]
   (a) & (b) & (c)\\
   \includegraphics[width=0.33\linewidth]{tuning/4.png} &
   \includegraphics[width=0.33\linewidth]{tuning/5.png} &
   \includegraphics[width=0.33\linewidth]{tuning/6.png} \\[-5pt]
   (d) & (e) & (f)\\
   \end{tabular}
 \end{center}
 \caption{Effect of fine tuning. (left) original image, (middle) initial detection, (right) continuous fine tuning}
 \label{fig:tuning}
\end{figure}

@@

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|c|c|c|c|c|}
   \hline
  \includegraphics[width=0.24\textwidth]{car_cnn/1a.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/1b.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/1c.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/1d.png}  \\  
   \hline
  \includegraphics[width=0.24\textwidth]{car_cnn/2a.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/2b.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/2c.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/2e.png}  \\  
   \hline
  \includegraphics[width=0.24\textwidth]{car_cnn/4a.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/4b.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/4c.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/4d.png}  \\  
%    \hline
%   \includegraphics[width=0.24\textwidth]{car_cnn/10a.png} &   
%   \includegraphics[width=0.24\textwidth]{car_cnn/10b.png} &   
%   \includegraphics[width=0.24\textwidth]{car_cnn/10c.png} &   
%   \includegraphics[width=0.24\textwidth]{car_cnn/10d.png}  \\  
%   \hline 
%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3a.png} &   
%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3b.png} &   
%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3c.png} &   
%   \includegraphics[width=0.24\textwidth]{bicycle_cnn/3d.png}  \\
  \hline
  \includegraphics[width=0.24\textwidth]{bicycle_cnn/7a.png} &   
  \includegraphics[width=0.24\textwidth]{bicycle_cnn/7b.png} &   
  &\\
  \hline
  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4a.png} &   
  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4b.png} &   
  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4c.png} &   
  \includegraphics[width=0.24\textwidth]{bicycle_cnn/4d.png}  \\
  \hline
  CNN Proposals & \multicolumn{3}{|c|}{Our matching results on proposal bounding boxes} \\
  \hline
\end{tabular}
\caption{Example enriched bounding boxex. Given R-CNN\cite{Girshick14} detection bounding boxes, our method predicted 2D-3D matching reasonably. On the first column, R-CNN detection bounding boxes overlaid. From the second to the last columns, output of our method given a R-CNN box. Blue boxes are R-CNN output and purle boxes are the tightest bounding box enclosing predicted CAD model}
  \label{fig:pascal12cnn}
\end{figure*}
